Interpreting Random Forest Predictions for Firearm Identification Using LIME

### 2019-06-12 papers/Interpreting Random Forest Predictions for Firearm Identification Using LIME/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
more work on cleaning repo

```{r setup, include = FALSE}
# Set knitr options
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, 
                      fig.pos = "center")

# Load libraries
library(bulletr)
library(cowplot)
library(furrr)
library(future)
library(lime)
library(purrr)
library(randomForest)
library(tidyverse)
library(tree)

# Source functions
source("../code/helper_functions.R")
```

>>>>

```{r setup, include = FALSE}
# Set knitr options
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, 
                      fig.pos = "center")
```
